Splints of root systems for special Lie subalgebras

### 2014-12-17 AffineLieAlgebras/Splints/special-paper.tex
More work on multiplicity-free

We want to classify all the cases when branching coefficients coincide with weight multiplicities of
some other algebra representations. Such a coincidence is possible when the projection $\Delta'$ of
$\gf$ root system admits a splint $\Delta=\Delta_{\af}\cup \Delta_{\sfr}$. Projection of the root
system $\Delta'$ coincides with the projection of weight diagram of the adjoint representation of
algebra $\gf$ with the exception of zero weight. Adjoint representation of $\gf$ contains adjoint
representation of $\af$ and can be decomposed as
\begin{equation}
  \label{eq:3}
  \mathrm{ad}_{\gf}=\mathrm{ad}_{\af}\oplus M_{\af}^{\chi},
\end{equation}
where $M^{\chi}_{\af}$ is not necessary irreducible representation of $\af$ called
``characteristic'' in \cite{dynkin1952semisimple}.

@@

@@

What we really need is the classification of all the representations where multiplicities of all
non-zero weights are equal to one. Fortunately, such a classification was obtained in
\cite{plotkin1998visual}. It consists of multiplicity-free representations and adjoint
representations of algebras $B_{r}$.

 (Possibly, strongly multiplicity-free:
).

 Classification of strongly multiplicity-free representations is simple:
$A_{n}$ first fundamental representation, $B_{n}$ first fundamental representation, $C_{n}$ first
fundamental representation, $G_{2}$ first fundamental representation (7) and
all irreducible $A_{1}$-representations.

>>>>

We want to classify all the cases when branching coefficients coincide with weight multiplicities of
some other algebra representations. Such a coincidence is possible when the projection $\Delta'$ of
$\gf$ root system admits a splint $\Delta'=\varphi_{\af}(\Delta_{\af})\cup
\varphi_{\sfr}(\Delta_{\sfr})$, where $\varphi_{\af}$ and $\varphi_{\sfr}$ are the embeddings of
corresponding root systems. The embedding $\varphi_{\af}$ is metric and trivial. Projection of the
root system $\Delta'$ coincides with the projection of weight diagram of the adjoint representation
of algebra $\gf$ with the exception of zero weight. Adjoint representation of $\gf$ contains adjoint
representation of $\af$ and can be decomposed as
\begin{equation}
  \label{eq:3}
  \mathrm{ad}_{\gf}=\mathrm{ad}_{\af}\oplus M_{\af}^{\chi},
\end{equation}
where $M^{\chi}_{\af}$ is not necessary irreducible representation of $\af$ called
``characteristic'' in \cite{dynkin1952semisimple}.

@@

First fundamental representation of $C_{r}$ -?

Projection $\Delta'$ on the subalgebra $A_{1}$ is never multiplicity free, so $\Delta_{\sfr}$ always
contain parallel roots. The simplest case is special embedding $A_{1}\to A_{2}$ where
$\Delta_{\sfr}$ is the root system $BC_{1}$. Such systems do not correspond to semisimple Lie
algebras, so we can not speak of a coincidence of branching coefficients for the reduction
$\gf\downarrow \af$ with weight multiplicities of $\sfr$-representations.

Weight diagram of of seven-dimensional representation of $G_{2}$ together with $G_{2}$ root system
form the projection of root system $B_{3}$ which appears in special embedding of simple Lie algebra
$G_{2}\to B_{3}$. Branching coefficients in this case coincide with weight multiplicities of
representations of algebra $\sfr=A_{2}$ with image of root system consisting of short roots of
$G_{2}$.

@@

The weight $\mu$ is minuscule if $\left<\mu,\alpha^{\vee}\right>\leq 1$ for all $\alpha\in
\Delta^{+}$.

Classification of multiplicity-free irreducible highest weight modules $L^{\mu}$ in
\cite{howe1995perspectives,stembridge2003multiplicity} consists of the following classes:
\begin{itemize}
\item (1) $\mu$ is minuscule,
\item (2) $\mu$ is quasi-minuscule and Lie algebra has only one short simple root,
\item (3) Lie algebra is $sp(6)$ and $\mu=\omega_{1}$, or
\item (4) Lie algebra is $sl(n + 1)$ and  $\mu= m\omega_{1}$ or $\mu  = m\omega_{n}$ 
\end{itemize}

We see that case (1) contains strongly multiplicity free modules of series $A_{r}, B_{r}, C_{r}$ and
exceptional Lie algebra $G_{2}$, strongly multiplicity free modules of $A_{1}$ are included in class
(4).

What we really need is the classification of all the representations where multiplicities of all
non-zero weights are equal to one. Fortunately, such a classification was obtained in
\cite{plotkin1998visual}. It consists of multiplicity-free representations and adjoint
representations of algebras $B_{r}, C_{r}$ and $F_{4}$.
